Imprecise Computing in Datapath Design: Precision Loss or Timing Violations

### 2013-04-24 TCAD2013/overclocking_tcad.tex
Modified CSA, revised by David v2

\section{Carry Select Adder}
\subsection{Introduction}
Since the delay of RCA is determined by the length of carry chain, the parallel adder architectures, such as carry select, carry look-ahead and Kogge-Stone adders, are proposed to boost the performance. For instance, the carry select adder (CSA) is designed with a carry chain being divided and overlapped in sections such that the operating speed can be largely increased. The structure of a CSA is shown in Fig.~\ref{Fig_CSA_Structure}. There are multiple stages within a CSA. Each stage contains two RCAs and two multiplexers, as seen in Fig.~\ref{Fig_CSA_SingleStage}. For a given input, two additions are performed simultaneously where the carry input is zero and one respectively. One of these two results is then selected according to the actual carry input. Although this structure brings performance benefits, it costs extra hardware resources compared to a standard RCA because the carry chain is duplicated. Furthermore, in FPGA technology, multiplexers are expensive. Due to this reason, we explore the trade-offs between silicon area, accuracy and performance of these two adder structures in this section.

\begin{figure}[htbp]
    \begin{minipage}[b]{.49\textwidth}
        \centering
        \subfigure[The structure diagram of a CSA with $s$ stages.]{
            \includegraphics[width=0.95\textwidth]{./Figures/CSA_structure.pdf}
            \label{Fig_CSA_Structure}
        }\vspace{-2ex}
        \subfigure[The structure of the $i^{th}$ stage in the CSA.]{
        %\centering
            \includegraphics[width=2.4in]{./Figures/CSA_SingleStage.pdf}
            \label{Fig_CSA_SingleStage}
        }
    \end{minipage}
    \centering
    \caption{A comparison between RCA and CSA in terms of the maximum word-length of input signal and the area consumption.}
\end{figure}

@@

\subsection{Timing Models for Carry Select Adder}
We initially model the CSA in order to understand the relationship between the operating frequency and the maximum word-length of the CSA. This information can then be employed to determine the truncation error based on the models presented in Section~\ref{section_RCA_TruncationError}.

In a CSA with $s$ stages~($s\geqslant 2$), let the stage delay be denoted by $d_{s-1}~\dots,~d_{0}$, where $d_{s-1}$ and $d_{0}$ represent the delay of the most significant and the least significant stages, respectively. In our analysis, we follow the assumption that the critical path delay is due to carry propagation and multiplexing the carry output. Note that unlike other stages, the least significant stage is only built by one RCA without multiplexers, since it is directly driven by the carry input. Hence we obtain the delay of the $i^{th}$ stage as presented in~(\ref{CSA_SingleStageDelay}), where $\mu_{c}$, $\mu_{mux}$ and $n_i$ denote the delay of $1$-bit carry propagation, the delay of multiplexing and the word-length of the $i^{th}$ stage of the CSA, respectively.
\begin{eqnarray}\label{CSA_SingleStageDelay}
  d_i=\left\{
    \begin{matrix}
      n_i\cdot \mu_{c}+(s-i)\cdot\mu_{mux}, &\textrm{if $i\in\left[1,s-1\right]$}\\
      n_0\cdot \mu_c + (s-1)\cdot\mu_{mux}, & \textrm{if $i=0$}
    \end{matrix}
  \right.
\end{eqnarray}

@@

Conventionally under a given frequency constraint, the word-length of RCA is truncated by using $n_{RCA}=b-1$ bits, where $b$ is determined by~(\ref{Max.length of carry chain}). Similarly for CSA, the word-length of each stage should be selected in order to satisfy~(\ref{TimingConstraint_CSA}).
\begin{eqnarray}\label{TimingConstraint_CSA}
  \begin{matrix}
    d_i\leqslant\frac{1}{f_s} &, & \forall i\in[0,s-1]
  \end{matrix}
\end{eqnarray}

@@

\subsection{Accuracy Benefits and Area Overhead in CSA}
We first verify the models for RCA and CSA in terms of the maximum word-length under the given operating frequencies. For the CSA, the ratio $\mu_{mux}/\mu_c$ can be computed from experiments. We perform post place-and-route simulations on the CSA with 2 stages using Xilinx Virtex-6 FPGA. The delay of the $i^{th}$ stage $d_i$ in~(\ref{CSA_SingleStageDelay}) is recorded with respect to different word-lengths of this given stage ($n_i$). The total word-length of CSA can be predicted through~(\ref{CSA_Timing}). In addition, the maximum word-lengths of the 2-stage CSA and RCA are obtained experimentally by increasing $n_{CSA}$ and $n_{RCA}$ respectively until errors are observed at the output. The comparison between the modeled value and the empirical results is illustrated in Fig.~\ref{Fig_CSA3stage_Timing} with dotted lines. It can be seen that our models for both RCA and CSA match well with the experimental results.

\begin{figure}[tbp]
    \begin{minipage}[b]{0.48\textwidth}
        \centering
        \subfigure[The modeled value and the experimental results of the maximum word-length of RCA and CSA.]{
            \centering
            \includegraphics[width=0.95\textwidth]{./Figures/CSA3stage_Model_Timing.eps}
            \label{Fig_CSA3stage_Timing}
        }
        \subfigure[Hardware resource usage for RCA and CSA with 2 and 3 stages.]{
            \centering
            \includegraphics[width=0.95\textwidth]{./Figures/CSA3stage_Area.eps}
            \label{Fig_CSA3stage_Area}
        }
    \end{minipage}
    \centering
    \caption{A comparison between RCA and CSA in terms of the maximum word-length of input signal and the area consumption.}
\end{figure}

As greater word-length corresponds to smaller truncation errors, we compare the maximum word-length of RCA and CSA with 2 stages and 3 stages over a range of operating frequencies, as presented in Fig.~\ref{Fig_CSA3stage_Timing}. It can be seen that in comparison to RCA, CSA achieves greater word-length when frequency is initially increased. RCA only outperforms than CSA when very high frequency is applied. This is because at low frequencies, although the multiplexer delay limits the word-length of each stage in CSA when compared to RCA, the stage parallelism in CSA enables a greater word-length. However when frequency increases, the multiplexer delay becomes comparable to the delay of the carry chain, and this inhibits the benefits of parallelism. In addition, we can see that the word-length of 3-stage CSA is always greater than 2-stage CSA across the entire frequency domain.

However, the accuracy benefits brought by CSA comes at the cost of a large area overhead. Fig.~\ref{Fig_CSA3stage_Area} depicts the number of Look-Up Tables (LUTs) in the FPGA used for all three structures. It can be seen that in order to meet a given frequency, the 3-stage CSA consumes $2.4\times\sim3.7\times$ area than RCA, while the 2-stage CSA requires $1.7\times\sim3.1\times$ extra area. This finding poses a question of which is the best adder structure for a specific area budget.

%\subsection{Exploring Trade-offs Between Accuracy, Performance and Area}
\section{The Optimum Adder Structure}
In Section~\ref{section_RCA}, we have discussed two design scenarios in RCA when considering timing constraints. In this section, we expand our analysis by incorporating the silicon area as another evaluation metric, and investigate the accuracy, performance and area trade-offs for different adder structures. In the conventional design scenario, the word-length of RCA and CSA is limited by the given frequency constraint, or/and the available hardware resources. The precision loss potentially generates large errors even without timing violations. However in the new design scenario, we use RCA with the maximum possible word-length under the given area budget, and the timing constraints are allowed to be violated. This process might result in timing errors as well as truncation errors due to area limitation. We compare these two scenarios with different design goals, with the aim of targeting the optimum design methodology under each situation.

@@

%Our results could be of interest to a circuit designer in two aspects. On one hand, it is desirable to create a circuit that can run at a given frequency with the minimum achievable output errors and resource usage. On the other hand, the algorithm designer will wish the circuit to operate as fast as possible with the minimum area whilst a certain error budget can be tolerated. We select the optimum design methodology for both situations.
\subsection{Determination of the Optimum Adder Structure for Given Frequency Requirements}
First, suppose the algorithm designer would wish to create a circuit that can run at a given frequency with the minimum achievable output errors and minimum resource usage. That is, a pair of $\{Area, Frequency\}$ constraint is applied. In this case, the optimum design method can be selected based on the following criteria:
\begin{itemize}
  \item Design with the minimum value of errors at outputs is the optimum design;
  \item If multiple designs achieve the same accuracy, then the design with minimum area is the optimum design;
  \item If both the accuracy and area are identical for multiple designs, they are all treated as the optimum design.
\end{itemize}

For instance, we record the mean value of error at outputs with respect to different operating frequencies for both design scenarios, when the number of the available LUTs is set to 25. The experimental results are shown in Fig.~\ref{CSA_LUT25}, on which the optimum adder structure is labeled. In the following experiments within this section, the input data are randomly generated following uniform distribution, in order to keep consistence with our models.
% sampled from a 16-bit data set, which is uniformly distributed.
\begin{figure}[th]
  \centering
  \includegraphics[width=3.3in]{./Figures/Error_LUT25.eps}
  \caption{A comparison between two design scenarios when the number of available LUT is 25. The RCA and CSA are investigated in the conventional scenario, while the RCA is explored in the proposed new scenario. The results are obtained from post place-and-route simulations on Xilinx Virtex-6 FPGAs.}
  \label{CSA_LUT25}
\end{figure}

We first notice that for all frequency values, the overclocked RCA achieves smaller error expectation than the RCA with truncated operand word-lengths, as predicted by the models for RCA in Section~\ref{section_RCA_Comparison}. It can also be observed that CSA cannot be implemented with the original word-length due to the limited area budget, and this leads to large truncation errors initially.

We then perform the similar experiments with a variety of area constraints. The optimum design methods with respect to different operating frequencies and area consumptions are demonstrated in Fig.~\ref{Fig_CSA_Tradeoff}. From this figure, several observations can be made. Firstly, if the available area is large enough to implement a CSA in full precision, it will be the optimum design. This is expected from our earlier analysis in Fig.~\ref{Fig_CSA3stage_Timing}. Secondly, the 2-stage CSA is better than the 3-stage CSA when frequency is initially increased, as it consumes less area although both of them achieve the same error expectation. Thirdly, only part of the CSA can be implemented if under a tighter area budget, whereas the RCA still keeps full precision. In this case, area becomes the dominate factor and precision is lost for the CSA. We see the RCA with overclocking is the optimum design method across almost the whole frequency domain in this situation. Last but not the least, for a more stringent area constraint, the word-length of RCA is also limited. This results in truncation errors initially for all design scenarios. However, the RCA with overclocking can still be employed as the optimum design, because it loses less precision than CSA under the same area constraint.
\begin{figure}[t]
  \centering
  \includegraphics[width=3.5in]{./Figures/Tradeoff.eps}
  \caption{A demonstration of the optimum design methodology which achieves the minimum error at outputs with respect to a variety of frequency and area constraints.}
  \label{Fig_CSA_Tradeoff}
\end{figure}

\subsection{Determination of the Optimum Adder Structure for Given Accuracy Requirements}
If the design goal is to operate the circuit as fast as possible with the minimum area whilst a certain error budget can be tolerated, the optimum design methodology can be decided as illustrated in Fig.~\ref{Fig_CSA_Tradeoff_Error}. In this situation, the error specifications are evaluated in terms of the mean relative error (MRE), as fiben by~(\ref{MRE}), where $E_{error}$ and $E_{out}$ refer to the mean value of error and the mean value of outputs, respectively.
\begin{eqnarray}\label{MRE}
  MRE=\left|\frac{E_{error}}{E_{out}}\right|\times 100\%
\end{eqnarray}

In our experiments, MRE is set ranging from $0.001\%$ to $50\%$. For a certain value of MRE, the design with the maximum operating frequencies is selected as the optimum design. Moreover, the smallest design is the optimum one if multiple structures operate at the same frequency, with a certain area requirement. Fig.~\ref{Fig_CSA_Tradeoff_Error} can thus be obtained based on these criteria.
%Based on these criteria, the decision graph is depicted in
%We also notice that for small frequencies, RCA with either overclocking or truncation of word-length of the input signal is the best design choice for any area constraint, since
\begin{figure}[t]
    \centering
    \includegraphics[width=3.5in]{./Figures/Tradeoff_Error.eps}
    \caption{A demonstration of the optimum design methodology which runs at the fastest frequency with respect to a variety of accuracy and area constraints.}
    \label{Fig_CSA_Tradeoff_Error}
\end{figure}

@@

\subsection{Design Guidance}
To sum up, the experiments reveal that for both design goals, CSA is the best option only when there is enough hardware resources. However this circumstance is unlikely to happen in the practice, especially with the continued technology scaling nowadays. Due to this reason, in the following sections we will focus on the situation where the hardware resources are limited, and therefore RCA is the design option in our following analysis and experiments.

>>>>

\section{Carry Select Adder}
\subsection{Introduction}
Since the delay of RCA is determined by the length of carry chain, alternative adder architectures, such as carry select adder (CSA) have been proposed to boost performance. For CSA, the carry chain is divided into multiple overlapped sections to increase the operating speed, as shown in Fig.~\ref{Fig_CSA_Structure}. There are multiple stages within a CSA. Each stage contains two RCAs and two multiplexers, as seen in Fig.~\ref{Fig_CSA_SingleStage}. For a given input, two additions are performed simultaneously where the carry input is zero and one respectively. One of these two results is then selected according to the actual carry input. Although this structure brings performance benefits, it costs extra hardware resources compared to a standard RCA because the carry chain is duplicated. Furthermore, in FPGA technology, multiplexers are expensive. Due to this reason, we explore the trade-offs between silicon area, accuracy and performance of RCA and CSA in this section.

\begin{figure}[htbp]
    \begin{minipage}[b]{.49\textwidth}
        \centering
        \subfigure[The structure diagram of a CSA with $s$ stages.]{
            \includegraphics[width=0.95\textwidth]{./Figures/CSA_structure.pdf}
            \label{Fig_CSA_Structure}
        }\vspace{-2ex}
        \subfigure[The structure of the $i^{th}$ stage in the CSA.]{
        %\centering
            \includegraphics[width=2.4in]{./Figures/CSA_SingleStage.pdf}
            \label{Fig_CSA_SingleStage}
        }
    \end{minipage}
    \centering
    \caption{The structure diagram of CSA.}
\end{figure}

@@

\subsection{Timing Models for Carry Select Adder}
We initially model the CSA in order to understand the relationship between the operating frequency and maximum word-length of the CSA. This information can then be employed to determine the truncation error based on the models presented in Section~\ref{section_RCA_TruncationError}.

%In a CSA, the stage delay refers to the combination of the carry propagation delay and the delay of multiplexing the carry output of the giv stage.

In our analysis, the stage delay of stage $i$ in the CSA refers to the combination of the $i$-bit carry propagation delay and the delay of multiplexing the carry output. For a CSA with $s$ stages~($s\geqslant 2$), let the stage delay be denoted by $d_{s-1},~\dots,~d_{0}$, where $d_{s-1}$ and $d_{0}$ represent the delay of the most significant and the least significant stages, respectively. We still follow the aforementioned assumption that the critical path delay of the CSA is due to carry propagation and multiplexing the carry output, instead of generating the sum outputs. It should be noted that unlike other stages, the least significant stage of the CSA is only built by one RCA without multiplexers, since it is directly driven by the carry input. Hence we can obtain the delay of the $i^{th}$ stage as presented in~(\ref{CSA_SingleStageDelay}), where $\mu_{c}$, $\mu_{mux}$ and $n_i$ denote the delay of $1$-bit carry propagation, the delay of multiplexing and the word-length of the $i^{th}$ stage of the CSA, respectively.
\begin{eqnarray}\label{CSA_SingleStageDelay}
  d_i=\left\{
    \begin{matrix}
      n_i\cdot \mu_{c}+(s-i)\cdot\mu_{mux}, &\textrm{if $i\in\left[1,s-1\right]$}\\
      n_0\cdot \mu_c + (s-1)\cdot\mu_{mux}, & \textrm{if $i=0$}
    \end{matrix}
  \right.
\end{eqnarray}

@@

Conventionally under a given frequency constraint, the word-length of RCA is truncated by using $n_{RCA}=b-1$ bits, where $b$ is determined by~(\ref{Max.length of carry chain}). Similarly for CSA, the word-length of each stage should be selected in order to satisfy~(\ref{TimingConstraint_CSA}).
\begin{eqnarray}\label{TimingConstraint_CSA}
  \begin{matrix}
    \forall i\in[0,s-1] &, & d_i\leqslant\frac{1}{f_s}
  \end{matrix}
\end{eqnarray}

@@

\subsection{Accuracy Benefits and Area Overhead in CSA}
We first verify the models for the RCA and CSA in terms of the maximum word-length under the given operating frequencies. For the CSA, the ratio $\mu_{mux}/\mu_c$ can be computed experimentally. We perform post place-and-route simulations on the CSA with 2 stages using Xilinx Virtex-6 FPGA. The delay of the $i^{th}$ stage $d_i$ in~(\ref{CSA_SingleStageDelay}) is recorded with respect to different word-lengths. The total word-length of CSA can be predicted through~(\ref{CSA_Timing}). In addition, the maximum word-lengths of the 2-stage CSA and RCA are obtained experimentally by increasing $n_{CSA}$ and $n_{RCA}$ respectively until errors are observed at the output. The comparison between the modeled value and the empirical results is illustrated in Fig.~\ref{Fig_CSA2stage_Timing} with dotted lines. It can be seen that our models for both RCA and CSA match well with the experimental results.

\begin{figure}[tbp]
    \begin{minipage}[b]{0.48\textwidth}
        \centering
        \subfigure[The modeled value and the experimental results of the maximum word-length of RCA and CSA.]{
            \centering
            \includegraphics[width=0.95\textwidth]{./Figures/CSA2stage_Model_Timing.eps}
            \label{Fig_CSA2stage_Timing}
        }
        \subfigure[Hardware resource usage for RCA and CSA with 2 and 3 stages.]{
            \centering
            \includegraphics[width=0.95\textwidth]{./Figures/CSA3stage_Area.eps}
            \label{Fig_CSA3stage_Area}
        }
    \end{minipage}
    \centering
    \caption{A comparison between RCA and CSA in terms of the maximum word-length of input signal and the area consumption.}
\end{figure}

%As greater word-length corresponds to smaller truncation errors, we compare the maximum word-length of RCA and CSA with 2 stages and 3 stages over a range of operating frequencies, as presented in

Fig.~\ref{Fig_CSA2stage_Timing} also highlight that in comparison to the RCA, the CSA achieves greater word-length when frequency is initially increased. The RCA only outperforms than the CSA when very high frequency is applied. This is because at low frequencies, although the multiplexer delay limits the word-length of each stage in CSA when compared to RCA, the stage parallelism in CSA enables a greater word-length. However when frequency increases, the multiplexer delay becomes comparable to the delay of the carry chain, and this inhibits the benefits of parallelism.
%In addition, we can see that the word-length of 3-stage CSA is always greater than 2-stage CSA across the entire frequency domain.

However, the accuracy benefits brought by CSA comes at the cost of a large area overhead. Fig.~\ref{Fig_CSA3stage_Area} depicts the number of Look-Up Tables (LUTs) in the FPGA used for a RCA, a 2-stage CSA and a 3-stage CSA. It can be seen that in order to meet a given frequency, the 3-stage CSA consumes $2.4\times\sim3.7\times$ area than RCA, while the 2-stage CSA requires $1.7\times\sim3.1\times$ extra area. This finding poses a question of which is the best adder structure for a specific area budget.

%\subsection{Exploring Trade-offs Between Accuracy, Performance and Area}
\section{Choosing the Optimum Adder Structure}
In Section~\ref{section_RCA}, we discussed two design scenarios for the RCA when considering timing constraints. In this section, we expand our analysis by incorporating silicon area as another evaluation metric, and investigate the accuracy, performance and area trade-offs for different adder structures. In the conventional design scenario, the word-length of RCA and CSA is limited by the given frequency constraint, or/and the available hardware resources. The precision loss potentially generates large errors even without timing violations. However in the new design scenario, we use the RCA with the maximum possible word-length under the given area budget, and the timing constraints are allowed to be violated. This process might result in timing errors as well as truncation errors due to area limitation. We compare these two scenarios with different design goals with the aim of finding the optimum design methodology under each situation.

@@

%Our results could be of interest to a circuit designer in two aspects. On one hand, it is desirable to create a circuit that can run at a given frequency with the minimum achievable output errors and resource usage. On the other hand, the algorithm designer will wish the circuit to operate as fast as possible with the minimum area whilst a certain error budget can be tolerated. We select the optimum design methodology for both situations.
\subsection{Determination of the Optimum Adder Structure for Given Frequency Requirements}
First, suppose the algorithm designer wished to create a circuit that can run at a given frequency with the minimum achievable output errors and minimum resource usage, i.e. a pair of $\{Area, Frequency\}$ constraint is applied. In this case, the optimum design method is selected according to the following criteria:
\begin{itemize}
  \item Design with the minimum mean value of errors at the output is the optimum design;
  \item If multiple designs achieve the same accuracy, then the design with minimum area is the optimum design;
  \item If both the accuracy and area are identical for multiple designs, they are all treated as the optimum design.
\end{itemize}

For instance, in Fig.~\ref{Fig_CSA_LUT25} we record the mean value of error at outputs with respect to different operating frequencies for both design scenarios when the number of the available LUTs is set to 25. In this graph, we have labeled the optimum adder structure. Note that in this and all the following experiments within this section, in order to apply our models the input data is randomly generated following the uniform distribution.

%, the input data are randomly generated following uniform distribution, in order to keep consistence with our models.

\begin{figure}[th]
  \centering
  \includegraphics[width=3.3in]{./Figures/Error_LUT25.eps}
  \caption{A comparison between two design scenarios when the number of available LUT is 25. The RCA and CSA are investigated in the conventional scenario, while the RCA is explored in the proposed new scenario. The results are obtained from post place-and-route simulations on Xilinx Virtex-6 FPGAs.}
  \label{Fig_CSA_LUT25}
\end{figure}

We first notice that for all frequency values, the overclocked RCA achieves smaller error expectation than the RCA with truncated operand word-lengths, as predicted by the models for the RCA in Section~\ref{section_RCA_Comparison}. It can also be observed that the CSA cannot be implemented with the original word-length due to the limited area budget and this leads to large truncation errors. Although CSA with 3 stages outperforms temporarily when frequency is further increased, the overclocked RCA is still the optimum design when high operating frequencies are applied.

We then perform similar experiments with a variety of area constraints. The optimum design methods with respect to different operating frequencies and area consumptions are demonstrated in Fig.~\ref{Fig_CSA_Tradeoff}. From this figure, several observations can be made. Firstly, if the available area is large enough to implement a CSA in full precision, it will be the optimum design. This is expected from our earlier analysis in Fig.~\ref{Fig_CSA2stage_Timing}. Secondly, the 2-stage CSA is better than the 3-stage CSA when frequency is initially increased, as it consumes less area although both achieve the same error expectation. Thirdly, only part of the CSA can be implemented under a tighter area budget, whereas the RCA still keeps full precision. In this case, area becomes the dominate factor and precision is lost for the CSA, meaning the RCA with overclocking is the optimum design method across almost the whole frequency domain in this situation. Last but not the least, for a more stringent area constraint, the word-length of RCA is also limited. This results in truncation errors initially for all design scenarios. However, the RCA with overclocking can still be employed as the optimum design, because it loses less precision than the CSA under the same area constraint.

\begin{figure}[t]
  \centering
  \includegraphics[width=3.5in]{./Figures/Tradeoff.eps}
  \caption{A demonstration of the optimum design methodology which achieves the minimum error at outputs with respect to a variety of frequency and area constraints.}
  \label{Fig_CSA_Tradeoff}
\end{figure}

\subsection{Determination of the Optimum Adder Structure for Given Accuracy Requirements}
If the design goal is to operate the circuit as fast as possible with the minimum area whilst a certain error budget can be tolerated, the optimum design methodology can be decided as illustrated in Fig.~\ref{Fig_CSA_Tradeoff_Error}. In this situation, the error specifications are evaluated in terms of the mean relative error (MRE), as given by~(\ref{MRE}), where $E_{error}$ and $E_{out}$ refer to the mean value of error and the mean value of outputs, respectively.
\begin{eqnarray}\label{MRE}
  MRE=\left|\frac{E_{error}}{E_{out}}\right|\times 100\%
\end{eqnarray}

In our experiments, MRE is set ranging from $0.001\%$ to $50\%$. For a certain value of MRE, the design with the maximum operating frequency is selected as the optimum design. Moreover, the smallest design is the optimum one if multiple structures operate at the same frequency, with a certain area requirement. Fig.~\ref{Fig_CSA_Tradeoff_Error} can thus be obtained based on these criteria.
%Based on these criteria, the decision graph is depicted in
%We also notice that for small frequencies, RCA with either overclocking or truncation of word-length of the input signal is the best design choice for any area constraint, since
\begin{figure}[t]
    \centering
    \includegraphics[width=3.5in]{./Figures/Tradeoff_Error.eps}
    \caption{A demonstration of the optimum design methodology which runs at the fastest frequency with respect to a variety of accuracy and area constraints.}
    \label{Fig_CSA_Tradeoff_Error}
\end{figure}

@@

\subsection{Design Guidance}
To sum up, the experiments reveal that for both design goals, CSA is the best option only when there is enough hardware resources. However for the remainder of this paper, we are interested in cases where there is a limited area budget, as may be the case in the embedded applications. Due to this reason, we will focus on the RCA in our following analysis and experiments.

%this circumstance is unlikely to happen in the practice, especially with the continued technology scaling nowadays. Due to this reason, in the following sections we will focus on the situation where the hardware resources are limited, and therefore RCA is the design option in our following analysis and experiments.
